---
output: 
  html_document: 
    df_print: kable
---
```{r "setup", include=FALSE}
library(dplyr)
library(pkgFunIndex)
work_dir = "C:/libraries/pkgFunIndex/work"
hist_df = readRDS(file.path(work_dir,"exp_fun_hist.Rds"))
cran_df = readRDS(file.path(work_dir,"cran.toc.rds")) %>%
  rename(pkg = Package, version = Version, date=Published) %>%
  semi_join(hist_df, by=c("pkg"))

hist_df = add_hist_fun_change_extra_cols(hist_df, cran_df)

```


# Overview of packages

```{r}
# Number of packages
n_distinct(cran_df$pkg)

# Average number of package versions
NROW(cran_df$pkg)
```


# Number of pkg versions 
```{r}
pkg_df = cran_df %>%
  group_by(pkg) %>%
  summarize(num_version = n()) %>%
  mutate(num_version = ifelse(num_version>=50,50, num_version))


hist(pkg_df$num_version,breaks=seq(-0.5,max(pkg_df$num_version)+0.5, by=1),xlim = c(0,50),main = "Distribution of number of package versions.", xlab="", ylab="")
```



# Overview of function updates

## Share of function versions that are changed in a certain way
```{r}
any.cols = c("args_changed","args_just_added", "breaking_change", "fun_is_added","fun_will_be_removed","fun_will_be_temporarily_removed")
all.cols = c("fun_is_fine")
cols = c(any.cols, all.cols)
hist_df %>%
  filter(version_num > 1) %>%
  summarize(
    across(all_of(cols),~mean(., na.rm=TRUE))
  ) %>%
  tidyr::pivot_longer(everything(), names_to ="measure", values_to = "share") %>%
  mutate(share = round(share*100,1))
```

## Share of functions that have some of the changes mentioned above

```{r}
hist_df %>%
  filter(version_num > 1) %>%
  group_by(pkg, fun) %>%
  summarize(
    across(all_of(any.cols),~any(., na.rm=TRUE)),
    across(all_of(all.cols),~any(., na.rm=TRUE))
  ) %>%
  ungroup() %>%
  summarize(
    across(all_of(cols),~mean(., na.rm=TRUE))
  ) %>%
  tidyr::pivot_longer(everything(), names_to ="measure", values_to = "share") %>%
  mutate(share = round(share*100,1))
```


## Share of package versions that have some of the changes mentioned above

```{r}
hist_df %>%
  filter(version_num > 1) %>%
  group_by(pkg, version) %>%
  summarize(
    across(all_of(any.cols),~any(., na.rm=TRUE)),
    across(all_of(all.cols),~any(., na.rm=TRUE))
  ) %>%
  ungroup() %>%
  summarize(
    across(all_of(cols),~mean(., na.rm=TRUE))
  ) %>%
  tidyr::pivot_longer(everything(), names_to ="measure", values_to = "share") %>%
  mutate(share = round(share*100,1))
```

## Share of packages that have some of the changes mentioned above

```{r}
hist_df %>%
  filter(version_num > 1) %>%
  group_by(pkg) %>%
  summarize(
    across(all_of(any.cols),~any(., na.rm=TRUE)),
    across(all_of(all.cols),~any(., na.rm=TRUE))
  ) %>%
  ungroup() %>%
  summarize(
    across(cols,~mean(., na.rm=TRUE))
  ) %>%
  tidyr::pivot_longer(everything(), names_to ="measure", values_to = "share") %>%
  mutate(share = round(share*100,1))
```


## Function names with breaking changes

```{r}
# Functions with breaking changes
breaking_change_df = filter(hist_df, breaking_change) %>%
  select(pkg, fun, args_str, prev_args_str)
NROW(breaking_change_df)
head(breaking_change_df, 20)
```


